Discrete Quantum Theories and Computing

### 2018-04-02 dissertation.tex
dissertation.lyx acknowledgments Updates...

\begin{acknowledgments}Thank Prof. Andrew J. Hanson, Prof. Gerardo
Ortiz, and Prof. Amr A. Sabry for publishing three papers \cite{geometry2013,DQT2014,THOS2017}
with me. They becomes the main part of my thesis, especially most
of Chapter~\ref{chap:DQT=000026DQC} is based on ``Geometry of discrete
quantum computing''~\cite{geometry2013} and ``Discrete quantum
theories''~\cite{DQT2014}; most of Chapter~\ref{chap:DQT=000026DQC}
is based on ``Quantum Interval-Valued Probability: Contextuality
and the Born Rule'' \cite{THOS2017}. Together with Prof. Dylan Paul
Thurston and Prof. Shouhong Wang, thank you for getting together to
understand what I did and passing my dissertation proposal Spring
2017. Also, you passed my Computer Science qualified exam Spring 2016.
Especially, my survey of real computation inspires me the comparison
of quantum computer and analog computer in Chapter~\ref{chap:Introduction}.
Thank Prof. Lawrence Moss for inviting me to presented my results
in the interdisciplinary logic seminar and SICE theory seminar, co-chairing
my Tier 3 committee, and drawing my attention on Prof. Abramsky's
paper~\cite{Abramsky2012}, which inspired me to merge quantum probability
with discrete quantum theories. Thanks John Gardiner for inspiring
discussion on the difficulties merging quantum probability with discrete
quantum theories~\cite{Gardiner2014}. An improved work consists
of Sec.~\ref{sec:Toward-IVPM} \end{acknowledgments}
\begin{abstract}
Our primary research interest is to build a quantum computing model
characterizing realistic quantum computers. While most of the quantum
computing models based on uncomputable numbers, that is, the continuum
of real numbers, most of the classical computers in our daily life
are digital instead of analog computers. This highlight the necessity
to investigate discrete models for quantum theory and computing. Specifically,
we start from replacing the continuum of complex numbers by the discrete
finite fields. Although we have fruitful results on their geometric
implications and computing powers, their probability models are still
not completely satisfactory. To address this issue, we further exploited
quantum interval-valued probability, and proved an imprecise version
of foundational results such as the Gleason and Kochen-Specker theorems.
\end{abstract}
\tableofcontents{}

>>>>

\begin{acknowledgments}Thank Prof. Andrew Hanson, Prof. Gerardo Ortiz,
and Prof. Amr Sabry for publishing three papers \cite{geometry2013,DQT2014,THOS2017}
with me. They becomes the main part of my thesis, especially most
of Chapter~\ref{chap:DQT=000026DQC} is based on ``Geometry of discrete
quantum computing''~\cite{geometry2013} and ``Discrete quantum
theories''~\cite{DQT2014}; most of Chapter~\ref{chap:DQT=000026DQC}
is based on ``Quantum Interval-Valued Probability: Contextuality
and the Born Rule'' \cite{THOS2017}. Together with Prof. Dylan Thurston
and Prof. Shouhong Wang, thank you for getting together to understand
what I did and passing my dissertation proposal Spring 2017. Also,
thank Prof. Dylan Thurston for serving in my advisory committee and
my Tier 3 committee, with other advisory committee members passing
my Computer Science qualifying exam Spring 2016. Especially, my survey
of real computation in the qualifying exam inspires me the comparison
of quantum computer and analog computer in Chapter~\ref{chap:Introduction}.
Thank Prof. Lawrence Moss for inviting me to presented my results
in the interdisciplinary logic seminar and SICE theory seminar, co-chairing
my Tier 3 committee, writing an assessment letter for me, and drawing
my attention on Prof. Abramsky's paper~\cite{Abramsky2012}, which
inspired me to merge quantum probability with discrete quantum theories.
Thanks John Gardiner for inspiring discussion on the difficulties
merging quantum probability with discrete quantum theories~\cite{Gardiner2014}.
An improved work consists of Sec.~\ref{sec:Toward-IVPM} \end{acknowledgments}
\begin{abstract}
Our primary research interest is to build a quantum computing model
characterizing realistic quantum computers. While most of the quantum
computing models based on uncomputable numbers, that is, the continuum
of real numbers, most of the classical computers in our daily life
are digital instead of analog computers. This highlight the necessity
to investigate discrete models for quantum theory and computing. Specifically,
we start from replacing the continuum of complex numbers by the discrete
finite fields. Although we have fruitful results on their geometric
implications and computing powers, their probability models are still
not completely satisfactory. To address this issue, we further exploited
quantum interval-valued probability, and proved an imprecise version
of foundational results such as the Gleason and Kochen-Specker theorems.
\end{abstract}
\tableofcontents{}
